Deciphering enhancer rules underlying early human neuronal and neural crest development.

### 2025-03-27 manuscript.tex
add pcc for organoid v embryo
make sure figures are placed niceley

\documentclass[12pt,letterpaper]{article}
\usepackage[a4paper, total={7in, 10in}]{geometry}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{graphicx}
\usepackage{helvet}
\usepackage{authblk}
\usepackage{hyperref}
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{orcidlink} 
\usepackage[super,comma,sort&compress]  
   {natbib}\bibliographystyle{numbered}
% \usepackage[right]{lineno} \linenumbers

@@

the topic) across the organoid and embryo (\textbf{Fig. 1i}) with an average Pearson correlation coefficient of \textbf{X.X}

@@

\noindent\includegraphics[width=1.0\linewidth]{figures/main/Figure_1.png}

\subsection*{Figure 1. Human neural tube organoids recapitulate early neuronal and neural crest development}

\textbf{a}, Schematic. \textbf{b-c}, UMAP based on gene expression profiles of organoid (\textbf{b}) and embryo
(\textbf{c}) cells colored by cell type identify. \textbf{d-f}, UMAP based on gene expression profiles of organoid (top)
and embryo (bottom) cells types showing sub-clusters of neuronal progenitors (\textbf{d}), early differentiating neurons
(\textbf{e}) and neural crest (\textbf{f}) along with expression of indicated genes in red-green-blue color scale.
\textbf{g}, UMAP based on gene expression profiles of organoid (top; UMAP axis 1 and 2 shown) and embryo (bottom; UMAP
axis 2 and 3 shown) for neuronal progenitor subcluster along with the expression of indicated genes in red-green-blue
color scale. \textbf{h}, UMAP based on gene expression profiles in organoid (top left) and embryo (top right) colored by
cell cycle phase identity and quantification of percentage of each cell for each cell cycle phase stratified by cell
type in the organoid (bottom left) and embryo (bottom right). \textbf{i}, Average gene expression level in
$log_{2}(CPM)$
(dot color) and fraction of cells expressing the gene (dot size) per cell state, defined by topic modeling, for organoid
cells (top) and embryo cells (middle) and motif enrichment level as normalized enrichment score (NES; dot color) and
number of regions enriched for the motif (dot size) per topic (x-axis) and motif (y-axis; bottom). PVM/MIC: perivascular
microphage/microglia.

@@

\noindent\includegraphics[width=1.0\linewidth]{figures/main/Figure_2.png}

\subsection*{Figure 2. DeepNeuralTube: an accurate sequence-to-function model revealing neuro-developmental enhancer
code.}
\textbf{a}, Schematic. \textbf{b} receiver-operator curves for identifying neural tube (left) and facial mesenchyme the
$DeepNeuralTube_{organoid}$ and $DeepNeuralTube_{embryo}$. \textbf{c-e}, UMAP of TomTom [REF] motif-to-motif similarities
using both \textit{de novo} motifs from DeepNeuralTube and known enriched motifs. Each dot is a motif. Motifs are
colored by: cluster identity (\textbf{c}), model of origin (\textbf{d}; only showing \textit{de novo} motifs in this
case) and whether the motif is found \textit{de novo} (Deep Learning) or by motif enrichment (cisTarget; \textbf{e}).
\textbf{f}, Example representative motifs from clusters in b, showing motifs from motif enrichment (left) and found
\textit{de novo} (right). \textbf{g}, contribution score for reference and mutant version of Vista enhancer hs111
for $DeepNeuralTube_{organoid}$ (top two panels) and $DeepNeuralTube_{embryo}$ (bottom two panels) and enhancer-reporter
assay for reference and mutant version of hs111 (right two panels) [REF]. \textbf{h}, contribution score for
$DeepNeuralTube_{organoid}$ (top) and $DeepNeuralTube_{embryo}$ (bottom) of a genomic enhancer human neural crest
enhancer (chr ...; hg38) and enhancer-reporter assay in chicken embryo (HH4; right). Green is enhancer signal, pink is
constitutive enhancer that serves as electroporation control.

@@

\noindent\includegraphics[width=1.0\linewidth]{figures/main/Figure_3.png}

\subsection*{
  Figure 3. Deciphering the enhancer code underlying dorso-ventral patterning of neuronal progenitors.
}
\textbf{a}, UMAP of organoid (top) and embryo (bottom) neuronal progenitors colored by cell-topic probabilities in RGB color scales of dorso-ventral topics. \textbf{b}, Boxplots of the expression of \textit{SHH} in organoid (top) and embryo (bottom) across different dorso-ventral topics ($n_{topic 33}$ = X, $n_{topic 38}$ = X, $n_{topic 36}$ = X, $n_{topic 54}$ = , and $n_{topic 48}$ = for organoid cells; and $n_{topic 34}$ = X, $n_{topic 38}$ = X, $n_{topic 79}$ = X, $n_{topic 88}$ = , and $n_{topic 58}$ = for embryo cells). \textbf{c}, Chromatin accessibility in organoid (top) and embryo (bottom) across dorso-ventral topics for locus chr:...-...; hg38. SFPE2 and SFPE1 is highlighted. \textbf{d}, Nucleotide contribution scores for SFPE2 (left) and SFPE1 (right) for organoid topic 33 (top) and embryo topic 34 (bottom). \textbf{e}, Code table showing average contribution score of pattern instances for each dorso-ventral topic. Contribution scores for $DeepNeuralTube_{organoid}$ are not outlined. Contribution scores for $DeepNeuralTube_{embryo}$ are outlined and negated. \textbf{f}, Heatmap showing the maximum normalized contribution score for each of the top 1,000 regions per topic (y-axis) and pattern (x-axis) for dorso-ventral topics. \textbf{g}, Heatmap showing scaled expression of transcription factors corresponding to identified patterns in organoid (left) and embryo (right) dorso-ventral topics. \textbf{h}, Heatmap showing Jaccard index of regions based on the presence of instances of the identified patterns. \textbf{i}, Scaled average and normalized number of cut sites (black, top) and contribution score (red, top) across genomic regions with a FOXA2 instance and heatmap showing normalized number of cut sites (bottom) for individual regions with a FOXA2 instance. Signal is centered on the FOXA2 instance start position. \textbf{j}, Bar chart showing the fraction of genomic regions that has a given number of FOXA2 instances for FOXA2 regions that overlap with HepG2 or A549 FOXA2 ChIp-seq signal (general; bottom) and those regions that don't overlap (specific; top). \textbf{k}, Boxplot (ADD NUMEBRS) showing $-log_10(p value)$ of FOXA2 motif hits calculated using FIMO\cite{grantFIMOScanningOccurrences2011,schreiberTangermemeBiologicalSequence2025} for general regions (bottom) and specific regions (top) stratified by the number of FOXA2 instance per region. \textbf{l}, \textit{de novo} motif for regions with a single FOXA2 instance that are specific (left, top) or general (right, top) and heatmap color coded by nucleotide identity for individual regions for both specific (left, bottom) and general (right, bottom) regions that have a single FOXA2 instance.

@@

\noindent\includegraphics[width=1.0\linewidth]{figures/main/Figure_4.png}

\subsection*{
Figure 4. A simple enhancer code underlies anterior-posterior patterning in neuronal progenitors.
}
\textbf{a}, UMAP of embryo neuronal progenitors colored by cell-topic probabilities in RGB color scales for
anterior-posterior topics. \textbf{b}, Heatmap showing pairwise pearson correlation coefficients of region-topic probabilities for dorso-ventral and anterior-posterior topics. \textbf{c}, Heatmap showing region-topic probabilities for the top 3,000 regions per topic (y-axis) and each anterior-posterior topic (x-axis). \textbf{d}, Heatmap showing prediction scores of $DeepNeuralTube_{embryo}$ on the topic 3,000 regions per topic (y-axis) for each anterior-posterior topics (x-axis).\textbf{e}, Heatmap showing the log of the number of seqlets for each identified pattern (y-axis) for all anterior-posterior topics (x-axis).\textbf{f}, Boxplot showing prediction score before (wt) and after (alt) substituting all instances of \textit{CTAATTAG} with \textit{CTAATCCCT} (top) or substituting all instances of \textit{CTAATCCCT} with \textit{CTAATTAG} (bottom) in the topic 3,000 regions of either Topic 61 or Topic 31. \textbf{g}, Boxplot showing prediction scores for all anterior-posterior topics after embedding 0 to 5 instances of \textit{CTAATTAG} while optimizing their location for Topic 61 (top) and after embedding 0 to 5 instances of \textit{CTAATCCCT} while optimzing their location for Topic 31 (bottom); n = 200. \textbf{h}, Boxplot showing prediction scores for all anterior-posterior topics after embedding 0 to 5 instances of \textit{CTAATTAG} while optimizing their location for Topic 31 (top) and after embedding 0 to 5 instances of \textit{CTAATCCCT} while optimzing their location for Topic 61 (bottom); n = 200. .\textbf{i}, receiver-operator curve (ROC) (top) and precision-recall curve (bottom) for logistic regression classifier classifying genomic regions as either Topic 61 or Topic 31 based on motif scores for \textit{CTAATTAG} and \textit{CTAATCCCT} motifs.

@@

\noindent\includegraphics[width=1.0\linewidth]{figures/main/Figure_5.png}

\subsection*{
  Figure 5. Deciphering the enhancer code underlying pre-migratory and migratory neural crest and facial mesenchyme.
}
\textbf{a}, UMAP of organoid (top two) and embryo (bottom two) neural crest cells colored by cell-topic probabilities in RGB color scales for neural crest related topics. \textbf{b}, Code table showing average contribution score of pattern instances for each neural crest related topic. Contribution scores for $DeepNeuralTube_{organoid}$ are not outlined. Contribution scores for $DeepNeuralTube_{embryo}$ are outlined and negated. \textbf{c}, Heatmap showing the maximum normalized contribution score for each of the top 1,000 regions per topic (y-axis) and pattern (x-axis) of neural crest related topics. \textbf{d}, Heatmap showing scaled expression of transcription factors corresponding to identified patterns in organoid (left) and embryo (right) for neural crest related topics. \textbf{e}, Heatmap showing Jaccard index of regions based on the presence of instances of the identified patterns. \textbf{f}, Manhattan plot showing -log p value of the SNP being associated with variations in facial shape\cite{whiteInsightsGeneticArchitecture2021} (positive y-axis) and the maximum (across classes of the model) of the absolute value of the difference in prediction score between the reference and alternative allele (negative y-axis; circles for $DeepNeuralTube_{organoid}$ and crosses for $DeepNeuralTube_{embryo}$) across the human genome. Lead SNPs are shown with a bigger dot size. \textbf{g}, Zoom in of chromosome one with the locus of SNP rs1555067 shown as an inset, the SNP itself is shown in red. \textbf{h}, Nucleotide contribution scores for Topic 58 of $DeepNeuralTube_{organoid}$ of the references (top) and alternative (bottom) allele of SNP rs1555067. The location of the SNP is indicated with a dotted line.

@@

\noindent\includegraphics[width=1.0\linewidth]{figures/main/Figure_6.png}

\subsection* {
  Figure 6. Deciphering the enhancer code of early neuronal differentiation.
}

\textbf{a}, UMAP of organoid (top two) and embryo (bottom two) differentiating neuron cells colored by cell-topic probabilities in RGB color scales for neuron related topics. \textbf{b}, Code table showing average contribution score of pattern instances for each neuron related topic. Contribution scores for $DeepNeuralTube_{organoid}$ are not outlined. Contribution scores for $DeepNeuralTube_{embryo}$ are outlined and negated. \textbf{c}, Heatmap showing the maximum normalized contribution score for each of the top 1,000 regions per topic (y-axis) and pattern (x-axis) of neuron related topics. \textbf{d}, Heatmap showing scaled expression of transcription factors corresponding to identified patterns in organoid (left) and embryo (right) for neuon related topics. \textbf{e}, Heatmap showing Jaccard index of regions based on the presence of instances of the identified patterns.

@@

\noindent\includegraphics[width=1.0\linewidth]{figures/main/Figure_7.png}

\subsection*{
  Figure 7. Neural tube cell states are encoded using four to five distinct transcription factor binding
  sites
}.
\textbf{a}, Area under the receiver-operator curve (outlined dots) and precision-recall curve of logistic regression
models classifying genomic regions to each topic using motif scores as features (top) and patterns with positive
coefficient for each logistic regression model along with the number of each patterns used for enhancer design
represented by the size of each dot (middle) and boxplots (n = 200) showing prediction score of designed enhancers for
each topic (bottom). \textbf{b}, heatmap showing prediction score for each topic of enhancers designed for all topics
for using $DeepNeuralTube_{organoid}$ (left) and $DeepNeuralTube_{embryo}$ (right). \textbf{c}, scatter plot showing
location of all pattern instances and contribution score at those locations, color is -log p value of the motif score
for each pattern calculated using FIMO\cite{grantFIMOScanningOccurrences2011, schreiberTangermemeBiologicalSequence2025} for organoid (top left) and embryo
(top right) and histograms showing the number of motif instances per 25 bp bins with confidence intervals indicated in
gray scales (black is +/- 1 standard deviation, gray is +/- 2 standard deviation and white is more than 3 standard
deviations) for organoid (bottom left) and embryo (bottom right).

\section*{DISCUSSION}

>>>>

\documentclass[12pt,letterpaper]{article}
\usepackage[a4paper, total={7in, 10in}]{geometry}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{graphicx}
\usepackage{helvet}
\usepackage{authblk}
\usepackage{hyperref}
\usepackage{amsmath} 
\usepackage{amssymb} 
\usepackage{orcidlink}
\usepackage{afterpage}
\usepackage{caption}
\usepackage[super,comma,sort&compress]  
   {natbib}\bibliographystyle{numbered}
% \usepackage[right]{lineno} \linenumbers

@@

the topic) across the organoid and embryo (\textbf{Fig. 1i}) with an average Pearson correlation coefficient of 0.892

@@

\afterpage{\clearpage}
\begin{figure}[p]
  \includegraphics[width=1.0\linewidth]{figures/main/Figure_1.png}
  \caption{
    \textbf{Human neural tube organoids recapitulate early neuronal and neural crest development.} \\
    \textbf{a}, Schematic. \textbf{b-c}, UMAP based on gene expression profiles of organoid (\textbf{b}) and embryo
    (\textbf{c}) cells colored by cell type identify. \textbf{d-f}, UMAP based on gene expression profiles of organoid (top)
    and embryo (bottom) cells types showing sub-clusters of neuronal progenitors (\textbf{d}), early differentiating neurons
    (\textbf{e}) and neural crest (\textbf{f}) along with expression of indicated genes in red-green-blue color scale.
    (Continues next page)
  }
\end{figure}
\afterpage{\clearpage}

\begin{figure}[b]
  \ContinuedFloat
  \caption*{\rule{\linewidth}{0.4pt}}
  \caption{
    (Continued) \textbf{g}, UMAP based on gene expression profiles of organoid (top; UMAP axis 1 and 2 shown) and embryo (bottom; UMAP
    axis 2 and 3 shown) for neuronal progenitor subcluster along with the expression of indicated genes in red-green-blue
    color scale. \textbf{h}, UMAP based on gene expression profiles in organoid (top left) and embryo (top right) colored by
    cell cycle phase identity and quantification of percentage of each cell for each cell cycle phase stratified by cell
    type in the organoid (bottom left) and embryo (bottom right). \textbf{i}, Average gene expression level in
    $log_{2}(CPM)$
    (dot color) and fraction of cells expressing the gene (dot size) per cell state, defined by topic modeling, for organoid
    cells (top) and embryo cells (middle) and motif enrichment level as normalized enrichment score (NES; dot color) and
    number of regions enriched for the motif (dot size) per topic (x-axis) and motif (y-axis; bottom). PVM/MIC: perivascular
    microphage/microglia.
  }
\end{figure}

@@

\afterpage{\clearpage}
\begin{figure}[p]
  \includegraphics[width=1.0\linewidth]{figures/main/Figure_2.png}
  \caption{
    \textbf{DeepNeuralTube: an accurate sequence-to-function model revealing neuro-developmental enhancer code.} \\
    \textbf{a}, Schematic. \textbf{b} receiver-operator curves for identifying neural tube (left) and facial mesenchyme the
    $DeepNeuralTube_{organoid}$ and $DeepNeuralTube_{embryo}$. \textbf{c-e}, UMAP of TomTom [REF] motif-to-motif similarities
    using both \textit{de novo} motifs from DeepNeuralTube and known enriched motifs. Each dot is a motif. Motifs are
    colored by: cluster identity (\textbf{c}), model of origin (Continues next page)
  }
\end{figure}
\afterpage{\clearpage}

\begin{figure}[b]
  \ContinuedFloat
  \caption*{\rule{\linewidth}{0.4pt}}
  \caption{
    (Continued) (\textbf{d}; only showing \textit{de novo} motifs in this case) and whether the motif is found \textit{de novo} (Deep Learning) or by motif enrichment (cisTarget; \textbf{e}).
 \textbf{f}, Example representative motifs from clusters in b, showing motifs from motif enrichment (left) and found
    \textit{de novo} (right). \textbf{g}, contribution score for reference and mutant version of Vista enhancer hs111
    for $DeepNeuralTube_{organoid}$ (top two panels) and $DeepNeuralTube_{embryo}$ (bottom two panels) and enhancer-reporter
    assay for reference and mutant version of hs111 (right two panels) [REF]. \textbf{h}, contribution score for
    $DeepNeuralTube_{organoid}$ (top) and $DeepNeuralTube_{embryo}$ (bottom) of a genomic enhancer human neural crest
    enhancer (chr ...; hg38) and enhancer-reporter assay in chicken embryo (HH4; right). Green is enhancer signal, pink is
    constitutive enhancer that serves as electroporation control.
  }
\end{figure}

@@

\afterpage{\clearpage}
\begin{figure}[p]
  \includegraphics[width=1.0\linewidth]{figures/main/Figure_3.png}
  \caption{
    \textbf{Deciphering the enhancer code underlying dorso-ventral patterning of neuronal progenitors.} \\
    \textbf{a}, UMAP of organoid (top) and embryo (bottom) neuronal progenitors colored by cell-topic probabilities in RGB color scales of dorso-ventral topics. \textbf{b}, Boxplots of the expression of \textit{SHH} in organoid (top) and embryo (bottom) across different dorso-ventral topics ($n_{topic 33}$ = X, $n_{topic 38}$ = X, $n_{topic 36}$ = X, $n_{topic 54}$ = , and $n_{topic 48}$ = for organoid cells; and $n_{topic 34}$ = X, $n_{topic 38}$ = X, $n_{topic 79}$ = X, $n_{topic 88}$ = , and $n_{topic 58}$ = for embryo cells). (Continues next page).
  }
\end{figure}
\afterpage{\clearpage}

\begin{figure}[b!]
  \ContinuedFloat
  \caption*{\rule{\linewidth}{0.4pt}}
  \caption{
    (Continued) \textbf{c}, Chromatin accessibility in organoid (top) and embryo (bottom) across dorso-ventral topics for locus chr:...-...; hg38. SFPE2 and SFPE1 is highlighted. \textbf{d}, Nucleotide contribution scores for SFPE2 (left) and SFPE1 (right) for organoid topic 33 (top) and embryo topic 34 (bottom). \textbf{e}, Code table showing average contribution score of pattern instances for each dorso-ventral topic. Contribution scores for $DeepNeuralTube_{organoid}$ are not outlined. Contribution scores for $DeepNeuralTube_{embryo}$ are outlined and negated. \textbf{f}, Heatmap showing the maximum normalized contribution score for each of the top 1,000 regions per topic (y-axis) and pattern (x-axis) for dorso-ventral topics. \textbf{g}, Heatmap showing scaled expression of transcription factors corresponding to identified patterns in organoid (left) and embryo (right) dorso-ventral topics. \textbf{h}, Heatmap showing Jaccard index of regions based on the presence of instances of the identified patterns. \textbf{i}, Scaled average and normalized number of cut sites (black, top) and contribution score (red, top) across genomic regions with a FOXA2 instance and heatmap showing normalized number of cut sites (bottom) for individual regions with a FOXA2 instance. Signal is centered on the FOXA2 instance start position. \textbf{j}, Bar chart showing the fraction of genomic regions that has a given number of FOXA2 instances for FOXA2 regions that overlap with HepG2 or A549 FOXA2 ChIp-seq signal (general; bottom) and those regions that don't overlap (specific; top). \textbf{k}, Boxplot (ADD NUMEBRS) showing $-log_10(p value)$ of FOXA2 motif hits calculated using FIMO\cite{grantFIMOScanningOccurrences2011,schreiberTangermemeBiologicalSequence2025} for general regions (bottom) and specific regions (top) stratified by the number of FOXA2 instance per region. \textbf{l}, \textit{de novo} motif for regions with a single FOXA2 instance that are specific (left, top) or general (right, top) and heatmap color coded by nucleotide identity for individual regions for both specific (left, bottom) and general (right, bottom) regions that have a single FOXA2 instance.
  }
\end{figure}

@@

\afterpage{\clearpage}
\begin{figure}[p]
  \includegraphics[width=1.0\linewidth]{figures/main/Figure_4.png}
  \caption{
    \textbf{A simple enhancer code underlies anterior-posterior patterning in neuronal progenitors.} \\
  \textbf{a}, UMAP of embryo neuronal progenitors colored by cell-topic probabilities in RGB color scales for
anterior-posterior topics. \textbf{b}, Heatmap showing pairwise pearson correlation coefficients of region-topic probabilities for dorso-ventral and anterior-posterior topics. \textbf{c}, Heatmap showing region-topic probabilities for the top 3,000 regions per topic (y-axis) and each anterior-posterior topic (x-axis). \textbf{d}, Heatmap showing prediction scores of $DeepNeuralTube_{embryo}$ on the topic 3,000 regions per topic (y-axis) for each anterior-posterior topics (x-axis).\textbf{e}, Heatmap showing the log of the number of seqlets for each identified pattern (y-axis) for all anterior-posterior topics (x-axis).\textbf{f}, Boxplot showing prediction score before (wt) and after (alt) substituting all instances of \textit{CTAATTAG} with \textit{CTAATCCCT} (top) or substituting all instances of \textit{CTAATCCCT} with \textit{CTAATTAG} (bottom) in the topic 3,000 regions of either Topic 61 or Topic 31. \textbf{g}, Boxplot showing prediction scores for all anterior-posterior topics after embedding 0 to 5 instances of \textit{CTAATTAG} while optimizing their location for Topic 61 (top) and after embedding 0 to 5 instances of \textit{CTAATCCCT} while optimzing their location for Topic 31 (bottom); n = 200. \textbf{h}, Boxplot showing prediction scores for all anterior-posterior topics after embedding 0 to 5 instances of \textit{CTAATTAG} while optimizing their location for Topic 31 (top) and after embedding 0 to 5 instances of \textit{CTAATCCCT} while optimzing their location for Topic 61 (bottom); n = 200. .\textbf{i}, receiver-operator curve (ROC) (top) and precision-recall curve (bottom) for logistic regression classifier classifying genomic regions as either Topic 61 or Topic 31 based on motif scores for \textit{CTAATTAG} and \textit{CTAATCCCT} motifs.
  }
\end{figure}
\afterpage{\clearpage}

@@

\afterpage{\clearpage}
\begin{figure}[p]
  \includegraphics[width=1.0\linewidth]{figures/main/Figure_5.png}
  \caption{
    \textbf{Deciphering the enhancer code underlying pre-migratory and migratory neural crest and facial mesenchyme.} \\
\textbf{a}, UMAP of organoid (top two) and embryo (bottom two) neural crest cells colored by cell-topic probabilities in RGB color scales for neural crest related topics. \textbf{b}, Code table showing average contribution score of pattern instances for each neural crest related topic. Contribution scores for $DeepNeuralTube_{organoid}$ are not outlined. Contribution scores for $DeepNeuralTube_{embryo}$ are outlined and negated. \textbf{c}, Heatmap showing the maximum normalized contribution score for each of the top 1,000 regions per topic (y-axis) and pattern (x-axis) of neural crest related topics. \textbf{d}, Heatmap showing scaled expression of transcription factors corresponding to identified patterns in organoid (left) and embryo (right) for neural crest related topics. \textbf{e}, Heatmap showing Jaccard index of regions based on the presence of instances of the identified patterns. \textbf{f}, Manhattan plot showing -log p value of the SNP being associated with variations in facial shape\cite{whiteInsightsGeneticArchitecture2021} (positive y-axis) and the maximum (across classes of the model) of the absolute value of the difference in prediction score between the reference and alternative allele (negative y-axis; circles for $DeepNeuralTube_{organoid}$ and crosses for $DeepNeuralTube_{embryo}$) across the human genome. Lead SNPs are shown with a bigger dot size. \textbf{g}, Zoom in of chromosome one with the locus of SNP rs1555067 shown as an inset, the SNP itself is shown in red. \textbf{h}, Nucleotide contribution scores for Topic 58 of $DeepNeuralTube_{organoid}$ of the references (top) and alternative (bottom) allele of SNP rs1555067. The location of the SNP is indicated with a dotted line.
  }
\end{figure}
\afterpage{\clearpage}

@@

\begin{figure}[b!]
  \noindent\includegraphics[width=1.0\linewidth]{figures/main/Figure_6.png}
  \captionsetup{justification=raggedright}
  \caption{ \textbf{Deciphering the enhancer code of early neuronal differentiation.}}
\end{figure}

\begin{figure}[b!]
  \ContinuedFloat
  \caption*{\rule{\linewidth}{0.4pt}}
  \caption{
  (Continued) \textbf{a}, UMAP of organoid (top two) and embryo (bottom two) differentiating neuron cells colored by cell-topic probabilities in RGB color scales for neuron related topics. \textbf{b}, Code table showing average contribution score of pattern instances for each neuron related topic. Contribution scores for $DeepNeuralTube_{organoid}$ are not outlined. Contribution scores for $DeepNeuralTube_{embryo}$ are outlined and negated. \textbf{c}, Heatmap showing the maximum normalized contribution score for each of the top 1,000 regions per topic (y-axis) and pattern (x-axis) of neuron related topics. \textbf{d}, Heatmap showing scaled expression of transcription factors corresponding to identified patterns in organoid (left) and embryo (right) for neuon related topics. \textbf{e}, Heatmap showing Jaccard index of regions based on the presence of instances of the identified patterns.}
\end{figure}

@@

\afterpage{\clearpage}
\begin{figure}[p]
  \includegraphics[width=1.0\linewidth]{figures/main/Figure_7.png}
  \caption{
    \textbf{Neural tube cell states are encoded using four to five distinct transcription factor binding sites} \\
\textbf{a}, Area under the receiver-operator curve (outlined dots) and precision-recall curve of logistic regression
models classifying genomic regions to each topic using motif scores as features (top) and patterns with positive
coefficient for each logistic regression model along with the number of each patterns used for enhancer design
represented by the size of each dot (middle) and boxplots (n = 200) showing prediction score of designed enhancers for
each topic (bottom). (Continues next page)}
\end{figure}
\afterpage{\clearpage}

\newpage
\vspace*{-\topskip}  
\begin{figure}[t]
  \ContinuedFloat
  %\caption*{\rule{\linewidth}{0.4pt}}
  \caption{
  (Continued)  \textbf{b}, heatmap showing prediction score for each topic of enhancers designed for all topics
for using $DeepNeuralTube_{organoid}$ (left) and $DeepNeuralTube_{embryo}$ (right). \textbf{c}, scatter plot showing
location of all pattern instances and contribution score at those locations, color is -log p value of the motif score
for each pattern calculated using FIMO\cite{grantFIMOScanningOccurrences2011, schreiberTangermemeBiologicalSequence2025} for organoid (top left) and embryo
(top right) and histograms showing the number of motif instances per 25 bp bins with confidence intervals indicated in
gray scales (black is +/- 1 standard deviation, gray is +/- 2 standard deviation and white is more than 3 standard
deviations) for organoid (bottom left) and embryo (bottom right).
}
\end{figure}

\clearpage
\section*{DISCUSSION}
